
% \hypertarget{chap: thanks}{Acknowledgments}
\phantomsection
% \addcontentsline{toc}{chapter}{\hyperlink{chap: thanks}{Acknowledgments}}
\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}
% \addcontentsline{toc}{chapter}{Acknowlegdments}

% 致谢
% 值此论文完成之际，谨在此向多年来给予我关心和帮助的老师、同学、朋友和家人表示衷心的感谢！

First of all, I would express my appreciations to my mentor Prof. Axel Mosig, who guides me into the field of bio-image processing, all my colleagues from the pattern recognition lab, who have been always sharing their leading-age algorithms and ideas with me, and all my classmates and friends for their kindly support.

For the \ac{IVFC} project, I would like to thank my collaborators Jin Guo, Guangda Liu, Xiaoying Tan, Dr. Yan Li, all being from Institutes of Biomedical Sciences (IBS), Fudan University, and Prof. Xunbin Wei from Med-X Research Institute of Shanghai Jiao Tong University. I also thank these two persons for guidance on signal processing and statistics: Dr. David Damm and Dr. Christian Fremerey, both of whom were graduated from Bonn University.

For the morphological image processing project, I would like to thank Prof. Weihua Tang from Shanghai Institute of Plant Physiology and Ecology (SIPPE, SIBS) for her kind help and professional suggestions. I would also thank the other collaborators Dr. Dong Zhang, Dr. Haikuan Liu, and Dr. Caiping Gui from SIPPE for their valuable work in obtaining the image data sets of pollen tubes.

I would also thank Dr. Zhi Yang from Institute Of Neuroscience (ION, SIBS) for his valuable neuron image data. Acknowledgments here also go to Dr. Xuewen Chen (ION), Dr. Yongchuan Zhu (ION) and Dr. Lin Li (SIPPE) for communications and help.

Last but not least, acknowledgments go to my family too!

% This study was supported by a Chinese Academy of Sciences Visiting Professorship for Senior International Scientists (grant no. 2011T1S11 to A.M.) and the National Natural Science Foundation of China (grant no. 30970266 to D.Z.)


